---
title: "Cocoa-Flavours"
output: html_notebook
---
---

##### Installing packages.
```{r}
# install.packages("readr")
#install.packages("ggplot2")
#install.packages('magrittr')
#install.packages("dplyr")
#install.packages("plyr")
```

##### Loading up the dataset

```{r}
library(readr)
chocolateData <- read_csv("/Users/amishra/DEV/Week9-ResearchProjects/R-Project/flavors_of_cacao.csv")
```

```{r}
head(chocolateData)
```

##### Connecting with database
##### MOngoDB
##### Calling mongolite library

```{r}
library(mongolite)
uri <- "mongodb://apoorva:apoorva@localhost:27017/chocolate"
con <- mongo(collection = "cocoa", db = "chocolate", url = uri)
```

##### Inserting the raw data to database for further analysis

```{r}
con$drop()
con$insert(chocolateData)
```

##### Query The database

```{r}
library(jsonlite)
library(datasets)
con$count('{}')
con$find()
```

##### Get the structure of data

```{r}
str(chocolateData)
```

##### Columns in the dataframe

```{r}
names(chocolateData)
```

##### Check if the the columns has a missing value

```{r}
sum(is.na(chocolateData))
```

##### Renaming the columns with spaces in it

```{r}
library(magrittr)
library(dplyr)
#library(tidyverse)
new_chocolateData <- chocolateData %>% 
                              rename(
                              Makers = Company...Maker.if.known.,
                              Recent_Review_Rating = REF
                              )
```
##### Check if the change that occured or not
```{r}
glimpse(new_chocolateData)
```
##### Remove the % sign for annalysis
```{r}
new_chocolateData$Cocoa.Percent <- sapply(new_chocolateData$Cocoa.Percent, 
                                          function(x) gsub("%", "", x))
new_chocolateData
```

```{r}
new_chocolateData <- type.convert(new_chocolateData)
class(new_chocolateData)
str(new_chocolateData)
```

##### Begin Analysis 
##### Average Rating over the years

```{r}
library(magrittr)
library(dplyr)
#detach('package':plyr, unload=TRUE)
avg_ratings <- new_chocolateData %>% 
  group_by(Review.Date) %>% 
 summarise(avg_ratings = mean(Rating), n_ratings = n())# Summary stats
avg_ratings
```
```{r}
conflicts()
```


##### Average Rating in each year
##### aes function used.
##### what I want to plot
##### what will be that data used for those

```{r}
library(ggplot2)
ggplot(data = new_chocolateData)
ggplot(new_chocolateData, aes(x = Rating, y = Review.Date)) +
geom_point()
```
##### specific bean origin
```{r}
unique(new_chocolateData$Broad.Bean.Origin)
```
##### specific bean and therir cocoa percentage
```{r}
library(ggplot2)
library(magrittr)
library(dplyr)
# groupby rating of cocoa 5,4, 3, 2, 1 on basis of review
group_by_bean <- new_chocolateData %>%
  group_by(Specific.Bean.Origin.or.Bar.Name)  %>%
  mutate(Cocoa_avg_Percent = mean(Cocoa.Percent))
group_by_bean
```
##### Plot
```{r}
ggplot(data = new_chocolateData) +
geom_point(mapping = aes(x = Specific.Bean.Origin.or.Bar.Name, y = Cocoa.Percent))
```
##### reviewers are giving less extreme scores.
##### calculating standard deviation
```{r}
standard_deviations <- 
  new_chocolateData %>% group_by(Review.Date) %>%
  summarise(count = dplyr::n(), avg = mean(Rating), sd = sd(Rating)) 
standard_deviations
```
##### extremes reviews decereased over the years 
##### plot sd
```{r}
ggplot(data = standard_deviations, mapping = aes(x = Review.Date, y = sd)) +
geom_line()
```
##### location of the company has an impact on the quality of the product.
```{r}
#library(plyr)
library(magrittr)
library(dplyr)
library(ggplot2)
group_by_loc <- new_chocolateData %>%
  group_by(Company.Location)  %>%
  filter(dplyr::n() > 10) %>% 
  mutate(avg = mean(Rating)) 
  ggplot(data = group_by_loc) + 
  geom_boxplot(mapping = aes(reorder(Company.Location, avg), Rating, fill = avg)) + 
  scale_fill_continuous(low = '#fffccc', high = '#fc4e2a', name = "Average rating") + 
  coord_flip() + 
  labs(x = 'Company Location', y = 'Rating') +
  expand_limits(y = c(0,5))
  group_by_loc
```
##### relationship between cocoa percentage and the chocolate’s rating.
```{r}
library(ggplot2)
new_chocolateData %>%
  ggplot(aes(x = Cocoa.Percent, y = Rating)) +
  geom_jitter(alpha = .75) + 
  coord_cartesian(ylim = c(0,5)) +
  labs(x = 'Cocoa percentage', y = 'Rating') + 
  theme_minimal() + 
  geom_smooth(method = 'lm', se = FALSE, col = 'red')
```
##### Most frequent bean origin
```{r}
library(plyr)
library(magrittr)
library(dplyr)
library(ggplot2)

new_chocolateData %>% 
  group_by(Broad.Bean.Origin) %>% # Group by origin
  filter(n() > 10) %>% # Limit to those with at least 10 observations
  mutate(count = n()) %>% # Add the count column
  ggplot(aes(x = reorder(Broad.Bean.Origin, count))) + 
  geom_bar() + 
  coord_flip() + 
  theme_minimal() + 
  labs(x = 'Bean origin', y = 'Count', title = 'Most frequently used broad bean origins')
```
##### origin of the bean have impact on the rating of the chocolate?
```{r}
new_chocolateData %>% 
  group_by(Broad.Bean.Origin) %>% 
  filter(n() > 10) %>% # Keep only those with more than 10 observations
  mutate(count = n()) %>%
  ggplot() + 
  geom_boxplot(aes(x = Broad.Bean.Origin, y = Rating)) + 
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 75, hjust = 1)) + 
  labs(x = 'Broad bean origin', y = 'Rating')
```


